---
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
params:
  title: "MetaboAnalyst Results"
  label: NULL
  clumps_ptm_results: NULL
  mapping_params: NULL
---

---
title: `r params$title`
---


```{r setup, include=FALSE}
# R tooles
library(tidyverse)
library(glue)
library(cmapR)
library(readxl)
library(yaml)
# library(plotly)
# library(DT) # for JS datatable features

# HTML / RMD tools
library(knitr)
library(htmltools)
library(kableExtra)

```

```{r import_data, include=FALSE}

# unlist clumps_ptm_tarfiles 
clumps_ptm_tars = unlist(strsplit(params$clumps_ptm_results, ","))

#### import panoply_nmf tarfile ####
results_dirs = list()
for (tarfile in clumps_ptm_tars) {
  if (!file.exists(tarfile)) stop(glue("Improperly formatted file-path '{tarfile}'"))
  
  dir = gsub("_clumps_ptm_full_results.tar$", "", basename(tarfile)) # get output prefix
  untar(tarfile, exdir = dir) # untar results in PWD
  
  results_dirs = c(results_dirs, dir)
}

## Import parameters
param_dir = results_dirs[[1]] # use params from the first set of results
# import parameter files
parameters = read_yaml(file.path(param_dir,"params.yaml"))
if (!is.null(params$mapping_params)) {
  parameters$mapping = read_yaml(params$mapping_params)
}


# counter variable for figures and tables
fig_count <- 1
tab_count <- 1

```


# Overview

This document describes the results of the Clumps-PTM workflow, which performs spatial analysis of PTM sites. The algorithm looks for clusters of differentially-regulated PTM sites on a given protein (i.e. '`r parameters$analysis$accession_col`'). 

For more information about the module please visit the [PANOPLY Wiki page](https://github.com/broadinstitute/PANOPLY/wiki/Data-Analysis-Modules%3A-panoply_clumps_ptm), or refer to the github for [ClumpsPTM](https://github.com/getzlab/CLUMPS-PTM/)


# Results


```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(DT::datatable(data = data.frame()))
```




```{js, echo=FALSE}
function filterImages(annotID) {
  var selectedGene = document.getElementById("gene-select-" + annotID).value.toLowerCase();
  <!-- var images = document.getElementsByClassName("pymol-img"); -->
  
  var container = document.getElementById("pymol-container-" + annotID);
  var images = container.getElementsByClassName("pymol-img");
  
  for (var i = 0; i < images.length; i++) {
    var gene = images[i].getAttribute("data-gene").toLowerCase();
    images[i].style.display = (selectedGene === "" || gene === selectedGene) ? "block" : "none";
  }
}
```


```{r results, results='asis', echo=FALSE, out.width='100%', out.height='50%'}

for(dir in results_dirs) {
  cat("  \n## ",  dir, "Results {.tabset}  \n")
  
  sub_dirs = list.files(dir, pattern = '_results$')
  figure_dir = file.path(dir, 'figures')
  
  #### Import Files #### 
  summary_fig = file.path(figure_dir, "clumpsptm_summary_figure.png")
  if (!file.exists(summary_fig)) stop(glue("Summary figure for '{dir}' results is missing."))
  
  dotplot_files = list.files(file.path(figure_dir, 'dotplots'), pattern = ".png")
  if (length(dotplot_files)==0) stop(glue("No dotplots found for '{dir}' results."))
  
  
  for(dotplot in dotplot_files) { # for each dotplot
    annot = gsub("_dotplot.png$","", dotplot)
    cat("  \n### ", annot, " \n")
    
    
    #### Dot Plots ####
    cat("\n#### Dotplots")
    
    cat(paste0("![Significant Protein Dotplot](", file.path(figure_dir, 'dotplots', dotplot), "){width=100%}"))
    cat("  \n")
    cat(glue("**Figure {fig_count}. {annot}** This dotplot shows the top protiens with clusters of differentially-regulated PTM sites in '{annot}'  samples. Positive results refer to proteins with clusters of upregulated PTMs, and negative results refer to proteins with clusters of downregulated PTMs."))
    cat("  \n")
    fig_count = fig_count+1 #increment figure counter
    
    
    
    #### Print Table ####
    cat("\n---\n")
    cat("\n#### Protein Structures\n")
    print(glue("Pymol figures for the top {parameters$postprocess$pymol_upper_limit} significant proteins in each test can be viewed below. Modifyable Pymol (.pse) files can be found in the 'figures/pymol/' directory of the results tarfile.\n"))
    
    ## load in files
    pymol_files = list.files(c(file.path(figure_dir, 'pymol', glue("{annot}_positive_results")),
                               file.path(figure_dir, 'pymol', glue("{annot}_negative_results"))),
                     pattern=".png", recursive = T, full.names = T) # pull any PNGs
    if (length(pymol_files)==0) {
      print(glue("\n**WARNING:** No PyMol figures found for '{annot}' results.\n"))
    } else {
      # compile pymol figure object
      pymol_list = lapply(pymol_files, function(fn) {
        res = list(fn = fn)
        bn = basename(fn) # get basename
        res$ptm = gsub(glue("^.+/([^_]+?)/PNGs/{bn}$"), "\\1", fn) # parse PTM type out of directory path
        res$gene = gsub(glue("^\\d+?_(.+?)_{res$ptm}.+?$"), "\\1", bn) # parse gene name out of 
        res$dir = gsub("^.+?_((positive)|(negative))_results.png$", "\\1", bn)
        return(res)
      })
      
      genes <- unique(unlist(lapply(pymol_list, function(x) {x$gene} ))) # get all unique genes
      
      ## create dropdown for each gene
      cat(paste(sep = "\n",
      '<label for="gene-select"><strong>Select a gene:</strong></label>',
      glue('<select id="gene-select-{annot}" onchange="filterImages(\'{annot}\')">'),
      '<option value="" selected disabled>Select a gene</option>'))
      for (gene in sort(genes)) {
        cat(glue('<option value="{gene}">{gene}</option>'))
      }
      cat(paste(sep = "\n",
      '</select>',
      #'<hr/>',
      glue('<div id="pymol-container-{annot}">')))
      
      ## add a divider for each pymol figure
      for (entry in pymol_list) {
        cat(paste(sep='\n',
                  glue('<div class="pymol-img" data-gene="{entry$gene}" data-direction="{direction}" data-ptm="{entry$ptm}" style="display:none; margin-bottom: 15px;">'),
                  glue('<p><strong>{entry$gene} ({direction}, {entry$ptm})</strong></p>'),
                  glue('<img src="{entry$fn}" style="max-width: 100%; border: 1px solid #ccc; padding: 5px;" />'),
                  '</div>'))
      }
      paste("</div>")
    }
    
    
    #### Print Datatables ####
    cat("\n---\n")
    cat("\n#### Data Tables")
    
    ## load in files
    datatables = list()
    
    ## wrangle and plot both datatables
    for (direction in c("positive", "negative")) {
      ## read in data
      datatable_fn = file.path(dir, glue("{annot}_{direction}_results"), "clumpsptm_output.tsv")
      if (!file.exists(datatable_fn)) {
        print(glue("WARNING: No {direction} result found for '{dir}' annotation '{annot}'"))
      } else datatables[[direction]] <- read.delim(datatable_fn)
      
      ## if we have data for this direction
      if (!is.null(datatables[[direction]])) { # if we have a datatable for this direction
        ## filter columns
        columns = c(parameters$analysis$accession_col, "geneSymbol", "uniprot", "pdb", "chain", "clumpsptm_sampler", "clumpsptm_pval", "clumpsptm_fdr", parameters$analysis$variable_sites_col)
        # print(setdiff(colnames(pos_table), columns))
        datatables[[direction]] = select(datatables[[direction]], columns) %>%
          rename("PTM-Type" = "clumpsptm_sampler",
                 "P-Value" = "clumpsptm_pval",
                 "FDR Value" = "clumpsptm_fdr")
        
        ## print datatables
        cat(glue("\n\n<details><summary><strong>{str_to_title(direction)} Results Table</strong></summary>\n\n"))
        # print(htmltools::tagList(DT::datatable(datatables[[direction]],
        DT::datatable(datatables[[direction]],
                      options = list(scrollX = TRUE, #pageLength = 10, 
                                     order = list(list(which(names(datatables[[direction]])=="FDR Value"), 'asc'))), # sort by nominal pval
                      caption = htmltools::tags$caption(
                        style = 'caption-side: top; text-align: left;',
                        htmltools::strong(glue::glue("Table {tab_count}.")),
                        glue::glue("Results for proteins with {direction}ly regulated PTM sites in {annot} samples."))
                      ) %>%
          formatStyle(parameters$analysis$variable_sites_col, "white-space" = "nowrap") %>%
          htmltools::tagList() %>% print()
        cat("\n</details>\n")
        tab_count <- tab_count + 1
      }
    }
    
  }
  
  cat("\n## {-}\n")
  cat("\n---\n")
  
  cat("\n## Summary of Analyzed Proteins\n")
  
  #### Print Summary Figure ####

  cat(paste0("![Number of Analyzed Proteins](", summary_fig, "){width=100%}"))
  cat("  \n")
  cat(glue("**Figure {fig_count}. {annot}** This figure shows the total number of analyzed proteins, as well as the number of significant proteins before and after FDR correction."))
  cat("  \n")
  fig_count = fig_count+1 #increment figure counter
  
  cat("\n---\n")
  cat("\n---\n")
}

```

***

# Parameters
    
Details about the parameters listed in **Table `r tab_count`** can be found in the [PANOPLY WIKI](https://github.com/broadinstitute/PANOPLY/wiki/Data-Analysis-Modules%3A-panoply_clumps_ptm).    
    
```{r params, results="asis", include=TRUE, echo=FALSE, warning=T, message=F}
tab_param <- data.frame(param=character(0), value=character(0)) # parameters are imported earlier

for (mod in names(parameters)) {
  param_set = parameters[[mod]] %>% # grab relevant parameter set
    lapply(function(p) { if(is.null(p)) { return("NULL") } else { return(p) } })
  tab_param <- data.frame(param=names(param_set), value=unlist(param_set))
  ## insert table
  tab_param %>%
    kbl(row.names =FALSE, caption=paste0('**Table ', tab_count,glue('**: List of parameters used in ```panoply_clumps_ptm``` ({mod} module).'))) %>%
    kable_paper('hover', full_width = F) %>%
    kable_styling(position = "left") %>%
    cat()
  cat("\n")

  ## increment
  tab_count <- tab_count + 1
}

if (length(results_dirs)>1) {
  print(glue("**NOTE:** Parameters taken from '{param_dir}' results directory. If multiple runs with different params were combined in this report, this will not be reflected in the parameters table."))
}
```

<br>

***

**_Created on `r Sys.time()`_**

***

<br>
