---
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
params:
  title: "MetaboAnalyst Results"
  label: NULL
  clumps_ptm_results: NULL
---

---
title: `r params$title`
---

# Overview

This document describes the results of the Clumps-PTM module, which performs spatial analysis of PTM sites.

The module looks for nearby clusters of differentially-regulated PTM sites on the same protein.
- Split into up / down-regulated
- Looks by isoform (DOUBLE CHECK)
- Phosphoproteome, Acetylome, Ubiquitylome, or Combined. Potentially flexible for other options

For more information about the module please visit the [PANOPLY Wiki page](https://github.com/broadinstitute/PANOPLY/wiki/Data-Analysis-Modules%3A-panoply_clumps_ptm), or refer to the github for [ClumpsPTM](https://github.com/getzlab/CLUMPS-PTM/)


```{r setup, include=FALSE}
# R tooles
library(tidyverse)
library(glue)
library(cmapR)
library(readxl)
# library(plotly)
# library(DT) # for JS datatable features

# HTML / RMD tools
library(knitr)
library(htmltools)
library(kableExtra)

```

```{r import_data, include=FALSE}

# unlist clumps_ptm_tarfiles 
clumps_ptm_tars = unlist(strsplit(params$clumps_ptm_results, ","))

#### import panoply_nmf tarfile ####
results_dirs = list()
for (tarfile in clumps_ptm_tars) {
  if (!file.exists(tarfile)) stop(glue("Improperly formatted file-path '{tarfile}'"))
  
  dir = gsub("_clumps_ptm_full_results.tar$", "", basename(tarfile)) # get output prefix
  untar(tarfile, exdir = dir) # untar results in PWD
  
  results_dirs = c(results_dirs, dir)
  
  # # locate necessary inputs from tar, and error if ANY are missing
  # log_file = list.files(path = tmpdir, pattern="*log_file.csv$") # locate combined GCT file
  # if (length(log_file) != 1) stop(glue("Tarfile {tarfile} is missing logfile of successfully analyzed annotations."))
  
  #### Finish Setup / File Import ####
  # # load in log file
  # log_file = read.csv(log_file)
  
  # # Get Analysis-Type from opt
  # anal_type = opt$anal_type
  # impact_metric = opt$impact_metric
  
}


# counter variable for figures and tables
fig_count <- 1
tab_count <- 1

```


# Results

```{r results, results='asis', echo=FALSE, out.width='100%', out.height='50%'}

for(dir in results_dirs) {
  cat("  \n## ",  dir, "Results {.tabset}  \n")
  
  sub_dirs = list.files(dir, pattern = '_results$')
  figure_dir = file.path(dir, 'figures')
  
  #### Import Files #### 
  summary_fig = file.path(figure_dir, "clumpsptm_summary_figure.png")
  if (!file.exists(summary_fig)) stop(glue("Summary figure for '{dir}' results is missing."))
  
  dotplot_files = list.files(file.path(figure_dir, 'dotplots'), pattern = ".png")
  if (length(dotplot_files)==0) stop(glue("No dotplots found for '{dir}' results."))
  
  pymol_files = list.files(file.path(figure_dir, 'pymol'))
  if (length(pymol_files)==0) print(glue("WARNING: No PyMol figures found for '{dir}' results."))
  
  
  for(dotplot in dotplot_files) { # for each dotplot
    annot = gsub("_dotplot.png$","", dotplot)
    cat("  \n### ", annot, " \n")
    
    #### Dot Plots ####
    cat(paste0("![Significant Protein Dotplot](", file.path(figure_dir, 'dotplots', dotplot), "){width=100%}"))
    cat("  \n")
    cat(glue("**Figure {fig_count}. {annot}** This dotplot shows ClumpsPTM results for the one-v-all comparison of the {annot} annotation."))
    cat("  \n")
    fig_count = fig_count+1 #increment figure counter
  }
  
  cat("\n---\n")
  cat("\n## {-}")
  #cat("\n## Summary of Analyzed Proteins\n")
  
  cat("\n")
  
  
  #### Print Summary Figure ####

  cat(paste0("![Number of Analyzed Proteins](", summary_fig, "){width=100%}"))
  cat("  \n")
  cat(glue("**Figure {fig_count}. {annot}** This figure shows the total number of analyzed proteins, as well as the number of significant proteins before and after FDR correction."))
  cat("  \n")
  fig_count = fig_count+1 #increment figure counter
  
  cat("\n---\n")
  cat("\n---\n")
}

```


***

# Parameters
    
Details about the parameters listed in **Table `r tab_count`** can be found in the [PANOPLY WIKI](https://github.com/broadinstitute/PANOPLY/wiki/Data-Analysis-Modules%3A-panoply_clumps_ptm).    
    
```{r params, include=TRUE, echo=FALSE, warning=T, message=F}
tab_param <- data.frame(param=character(0), value=character(0))
# tab_param <- data.frame(param=names(opt), value=unlist(opt))
## insert table
tab_param %>%
      kbl(row.names =FALSE, caption=paste0('**Table ', tab_count,'**: List of parameters used in ```panoply_clumps_ptm```.')) %>%
      kable_paper('hover', full_width = F) 
```
```{r echo=F}
## increment
tab_count <- tab_count + 1
```

<br>

***

**_Created on `r Sys.time()`_**

***

<br>
