---
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
params:
  title: "MetaboAnalyst Results"
  label: NULL
  metaboanalyst_results: NULL
---

---
title: `r params$title`
---

# Overview

This document describes the results of the MetaboAnalyst module, which performs metabolic analysis. For more information about the module please visit the [PANOPLY Wiki page](https://github.com/broadinstitute/PANOPLY/wiki/Data-Analysis-Modules%3A-panoply_metaboanalyst), or refer to the original [MetaboAnalyst](https://www.metaboanalyst.ca/home.xhtml) software.


```{r setup, include=FALSE}
# R tooles
library(tidyverse)
library(glue)
library(cmapR)
library(readxl)
# library(plotly)
# library(DT) # for JS datatable features

# HTML / RMD tools
library(knitr)
library(jsonlite)
library(htmltools)
library(kableExtra)

create_tmp_file=FALSE # set to TRUE to make JSON files, useful for testing in CodePen
send_df_to_js <- function(df, id="data"){ # send df to javascript variable in json format
  cat(
    paste(
    '<script>
      const ', id,' = ',toJSON(df),';
    </script>'
    , sep="")
  )
}

```

```{r import_data, include=FALSE}
#### import panoply_nmf tarfile ####
untar(params$metaboanalyst_results, exdir = getwd()) # untar results in PWD
# locate necessary inputs from tar, and error if ANY are missing
file_metaboanalyst_opt = list.files(pattern = 'metaboanalyst_opt.Rdata$') # locate Rdata object containing parameters
if (length(file_metaboanalyst_opt) != 1) stop(glue("Tarfile {params$metaboanalyst_results} is missing metaboanalyst_opt.Rdata object, containing parameters used in panoply_metaboanalyst."))
log_file = list.files(pattern="*log_file.csv$") # locate combined GCT file
if (length(log_file) != 1) stop(glue("Tarfile {params$metaboanalyst_results} is missing logfile of successfully analyzed annotations."))

#### Finish Setup / File Import ####
# load in panoply_metaboanalyst parameters
load(file_metaboanalyst_opt) # load opt list object (panoply_metaboanalyst. parameters)
# load in log file
log_file = read.csv(log_file)

# counter variable for figures and tables
fig_count <- 1
tab_count <- 1

```


```{r prep_data, include=FALSE}

xls_files = list.files(pattern = "_fullResults.xls")  # locate combined GCT file
if (length(xls_files) < 1) stop(glue("Tarfile {params$metaboanalyst_results} is missing XLS files with enrichment results."))

#### Create df_annot ####
df_annot = data.frame()
for (annot_of_interest in unique(log_file$annot.name)) {
# for (annot_of_interest in c("NMF.consensus.k3", "NMF.consensus.core.k3", "NMF.consensus.k6", "NMF.consensus.core.k6")) {
  log_file.tmp = filter(log_file, annot.name==annot_of_interest) %>% # check log for results
    column_to_rownames('subvalue.name') # set unique subvalue names to rownames, for easy lookup
  if (!any(log_file.tmp$valid.results)) next # skip if no annot has valid results
  
  # if there are valid results
  res_file = list.files(pattern = glue("_{annot_of_interest}_fullResults.xls$")) # all XLS results
  #write(res_file, file='/opt/input/tmp.txt', append=TRUE)
  # sheets <- readxl::excel_sheets(fn)
  
  for(value_of_interest.name in rownames(log_file.tmp)) {
    if(!log_file.tmp[value_of_interest.name,"valid.results"]) next # don't show invalid / blank subvalues
    value_of_interest = log_file.tmp[value_of_interest.name,"subvalue.value"] # get original annot value for use in analysis
    
    if( !(value_of_interest.name %in% readxl::excel_sheets(res_file)) ) {
      stop(glue("Annotation subvalue '{value_of_interest}' should have valid results, but does not appear in the fullResults spreadsheet for annotation '{annot_of_interest}'."))
    }
    
    df.tmp = readxl::read_xls(res_file, sheet = value_of_interest.name) %>%
      dplyr::rename(Pathway.ID = "...1") %>% # set first column to rownames
      dplyr::mutate(Annot = annot_of_interest,
                    Subvalue = value_of_interest) %>%
      dplyr::select(Annot, Subvalue, Pathway.ID, everything())
    df_annot = rbind(df_annot, df.tmp)
  }
}

#### Heatmap base64 Array ####
imgObj = list()
for (annot_of_interest in unique(log_file$annot.name)) {
  hm_file = list.files(pattern = glue("_{annot_of_interest}_heatmap.png$"))
  
  if (length(hm_file)==0) next # don't add anything if it doesn't exist
  imgObj[[annot_of_interest]] = knitr::image_uri(hm_file) # otherwise convert file to base64 and add to array 
}

```

```{r generate_jsons, echo=FALSE, results='asis'}
# Log File
send_df_to_js(log_file, id="log_file") # create JS variable log_file
if (create_tmp_file) { # create file for JavaScript testing in CodePen.io
  exportJSON <- toJSON(log_file)
  write_json(exportJSON, path="log_file.JSON")
  file.copy('log_file.JSON', '/opt/input/', overwrite=T)
}

# Results JSON
send_df_to_js(df_annot, id="json_annot") # create JS variable log_file
if (create_tmp_file) { # create file for JavaScript testing in CodePen.io
  exportJSON <- toJSON(df_annot)
  write_json(exportJSON, path="results.JSON")
  file.copy('results.JSON', '/opt/input/', overwrite=T)
}

# Image Array
send_df_to_js(imgObj, id='imgArr')
if (create_tmp_file) { # create file for JavaScript testing in CodePen.io
  exportJSON <- toJSON(imgObj)
  write_json(exportJSON, path="heatmaps.JSON")
  file.copy('heatmaps.JSON', '/opt/input/', overwrite=T)
}

# Network JSON
cat(paste(
  '<script>
    const json_network_str = ',read_file('networks.JSON'),';
  </script>', sep=""))
# Network Annotations JSON
network_annots_file = list.files(pattern="._network_annots.JSON$")
cat(paste(
  '<script>
    const json_net_anno_str = ',read_file(network_annots_file),';
  </script>', sep=""))


```



# Results


````{=html}
<!-- Load jquery.js -->
<script src="https://ajax.googleapis.com/ajax/libs/jquery/2.1.3/jquery.min.js"></script>
<!-- Load d3.js -->
<script src="https://d3js.org/d3.v4.js"></script>
<!-- Load DataTables -->
<link rel="stylesheet" href="https://cdn.datatables.net/2.1.8/css/dataTables.dataTables.css" />
<script src="https://cdn.datatables.net/2.1.8/js/dataTables.js"></script>

<div class="dropdown-menu" id="dropdown_menu">
  <select id="dropdown_annot">
  </select>
  <select id="dropdown_subvalue">
  </select>
</div>

<div class='parent'>
  <!-- Create a div where the graph will take place -->
  <div id="div_volcano" class='child flex-child'></div>


  <!-- Create a div where the graph will take place -->
  <div id="div_network" class='child flex-child'></div>
</div>
    
    
<table id="myTable" class="display">
    <thead>
      <tr id="table-headers">
        <!-- Column headers will be populated here dynamically -->
      </tr>
    </thead>
    <tbody>
        <!-- Data will be injected here dynamically -->
    </tbody>
</table>

<img width=100% height=100% name="img_heatmap" />
````



```{css, echo=FALSE}
* {
  margin: 0;
  padding: 0;
  box-sizing: border-box;
  font-family: "Inter", sans-serif;
  --shadow: rgba(0, 0, 0, 0.05) 0px 6px 10px 0px,
    rgba(0, 0, 0, 0.1) 0px 0px 0px 1px;
  --color: #166e67;
  --gap: 0.5rem;
  --radius: 5px;
}

body {
  margin: 2rem;
  font-size: 0.9rem;
  color: black;
}

.parent {
  display: flex;
  width: 100%;
}
.flex-child {
  flex: 1;
}

.dropdown-menu {
  position: relative;
  display: contents;
}

/* Tooltip style */
.tooltip {
  position: absolute;
  padding: 5px;
  background-color: #ddd;
  color: black;
  border-radius: 5px;
  pointer-events: none;
  opacity: 0;
  white-space: pre-wrap;
}
```

```{js, echo=FALSE}
//// ---- Data Wrangling


// parse Networks
const json_network = JSON.parse(json_network_str);
console.log(json_network)

// parse Network Annotations
const json_net_anno = JSON.parse(json_net_anno_str);
console.log(json_net_anno)


// temporarily set Impact Score statically
const impact_score = "Impact.BC"



//// ---- Utility Functions
function onlyUnique(value, index, array) {
  return array.indexOf(value) === index;
}
function getMax(arr, prop) {
  var max;
  for (var i=0 ; i<arr.length ; i++) {
    if (max == null || parseInt(arr[i][prop]) > parseInt(max))
      max = arr[i][prop];
  }
  return max;
}
function removeOptions(selectElement) {
   var i, L = selectElement.options.length - 1;
   for(i = L; i >= 0; i--) {
      selectElement.remove(i);
   }
}
// Function to merge two arrays based on matching `id`
function mergeJSONObjects(data1, data2, key) {
    return data1.map(item1 => {
        // Find the corresponding item from data2 by matching `id`
        const item2 = data2.find(item => item[key] === item1[key]);
        
        // If a matching item is found, merge them, otherwise return item1 as it is
        return item2 ? { ...item1, ...item2 } : item1;
    });
}
function dropItem(arr, item) {
  const index = arr.indexOf(item);
  if (index > -1) { // only splice array when item is found
    arr.splice(index, 1); // 2nd parameter means remove one item only
  }
  return arr
}

//// ---- Aesthetic Variables
// bounce_select animation
var bounce_select = d3.transition()
  .duration(1000)
  .ease(d3.easeElastic.period(0.4));
// define tooltips
var tooltip = d3.select("body").append("div")	
.attr("class", "tooltip")				
.style("opacity", 0);

//// ---- HTML Elements
const annotMenu = document.getElementById("dropdown_annot");
const subvalueMenu = document.getElementById("dropdown_subvalue");
//const toggleArrow = document.getElementById("arrow");





//// ---- Set Up Dropdown Menus
// get unique annot-values
const all_annots = log_file.map((entry) => entry['annot.name'])
const annots = all_annots.filter(onlyUnique)
// add annots to dropdown_annot
annots.forEach((entry, index, arr) => {
  annotMenu.options[annotMenu.options.length] = new Option(entry, index);
})
// -- Annot Change Event-Listener
annotMenu.addEventListener("change", function(event) {
  updateSubvalueMenu()
  updateHeatmap(annotMenu.options[annotMenu.selectedIndex].text)
  
  clearTable(table) // clear table if we change annot
  clearVolcano() // clear volcano if we change annot
  clearNetwork() // clear network if we change annot
});


// -- Update subvalue Menu                   
function updateSubvalueMenu() {
  // -- clear menu
  removeOptions(subvalueMenu)
  // -- add default value
  subvalueMenu.append( new Option(text="Select Annotation Subvalue",
                                  value="none"))
  subvalueMenu.options[0].disabled = true // set first valid result to selected
  subvalueMenu.options[0].hidden = true // set first valid result to selected
  subvalueMenu.options[0].selected = true // set first valid result to selected
  
  // -- get relevant subvalues
  var log_subvalue = log_file.filter((entry,index,arr) => entry["annot.name"]==annotMenu.options[annotMenu.selectedIndex].text)
  
  // -- add subvlues to subvalueMenu & format
  log_subvalue.forEach((entry, index, arr) => {
    // create new option for each subvalue
    //subvalueMenu.options[subvalueMenu.options.length] = new Option(entry['subvalue.value'], entry['subvalue.name']);
    subvalueMenu.append( new Option(text=entry['subvalue.value'],
                                    value=entry['subvalue.name']))
    
    // disable subvalue if no valid results
    subvalueMenu.options[index+1].disabled = !entry['valid.results'] // offset by 1 since we have a default
    
    //// select first valid option
    //var selected_index = arr.map((entry) => entry['valid.results']).findIndex(value => value === true) // get first valid result
    //subvalueMenu.options[index].selected = index===selected_index // set first valid result to selected
  });
  
  //console.log(subvalueMenu))
}
updateSubvalueMenu() // call to initialize
// -- Subvalue Change Event-Listener
subvalueMenu.addEventListener("change", function(event) {
  //console.log(event)
  updateVolcano(json_annot,
                annotMenu.options[annotMenu.selectedIndex].text,
                subvalueMenu.options[subvalueMenu.selectedIndex].text)
  updateDataTable(table, columnNames,
                  annotMenu.options[annotMenu.selectedIndex].text,
                  subvalueMenu.options[subvalueMenu.selectedIndex].text)
} );



//// ---- Heatmaps
function updateHeatmap(annot) {
    document.img_heatmap.src = imgArr[annot];
}
updateHeatmap(log_file[0]['annot.name']) //initialize with first annot

//// ---- Initialize DataTable
const columnNames = Object.keys(json_annot[0]) // Extract column names from annot-table
function clearTable(table) {
  // clear all the elements of the table by searching for NA, which should not exist
  table
    .column(columnNames.indexOf("Annot")).search('NA', { exact: true }) // search for NA
    .column(columnNames.indexOf("Subvalue")).search('NA', { exact: true })  // search for NA
    .draw()
}
function initializeDT(df, columnNames) {
  // Initialize Headers
  const tableHeaders = $('#table-headers');
  // Dynamically generate the table headers 
  columnNames.forEach(function(column) {
    tableHeaders.append('<th>' + column.charAt(0).toUpperCase() + column.slice(1) + '</th>'); // Capitalize first letter for display
  });
  
  // identify columns to hide
  let col_to_filt = ['Annot', 'Subvalue', 'Pathway.ID', 'Test.Type'] 
      .concat(dropItem(["Impact.BC", "Impact.CC", "Impact.DC"], impact_score))
  let filt_idx = [];
  col_to_filt.forEach(entry => filt_idx.push(columnNames.indexOf(entry)))
  // identify Raw.P.Value column
  const search_idx = columnNames.indexOf("Pathway.Name")
  const sort_idx = columnNames.indexOf("Raw.P.Value")
  
  // Initialize DataTables
  const table = new DataTable('#myTable', {
    scrollY: 300, // scroll height
    scrollCollapse: true, // collapse height if fewer entries
    paging: false,
    lengthChange: false,
    columnDefs: [
      { visible: false, targets: filt_idx }, // hide first three columns
      { searchable: true, targets: search_idx },
    ], 
    order: [sort_idx, 'asc'] // sort by p-value
  });
  
  // -- Populate the table body with data
  df_array = df.map( Object.values ); // convert to array of arrays
  table.rows.add(df_array).draw(); // add all arrays as rows & draw
  
  // hide all rows
  clearTable(table);
  
  return table
}
var table = initializeDT(json_annot, columnNames) // set table variable

//// ---- Update DataTable
function updateDataTable(table, columnNames, annot_filt, subval_filt) {
  table
    .column(columnNames.indexOf("Annot")).search(annot_filt, { exact: true })
    .column(columnNames.indexOf("Subvalue")).search(subval_filt, { exact: true })
    .draw()
}




//// ---- Update Volcano Plot
// function to remove volcano object
function clearVolcano() {
  if (document.getElementById("svg_volcano")) { document.getElementById("svg_volcano").remove() }
  if (document.getElementById("point_vals_volcano")) { document.getElementById("point_vals_volcano").remove() }
}
// function to create/update volcano plot
function updateVolcano(df, annot_filt, subval_filt) {
  y_val = "neg.Log.P.Value"
  x_val = impact_score
  // filter json to annot_filt
  const df_annot = df.filter((entry,index,arr) => entry["Annot"]===annot_filt )
  //console.log(json_annot)
  // further filter json to subval_filt
  const df_subv = df_annot.filter((entry,index,arr) => entry["Subvalue"]===subval_filt )
  
  // if we've already made the thing, remove it
  clearVolcano()
  
  // get width of container object
  const containerWidth = document.querySelector('.parent').offsetWidth
  const containerHeight = window.innerHeight
  
  // Declare the chart dimensions and margins.
  const width = containerWidth/2*0.95;
  const height = containerHeight/3;
  const marginTop = 20;
  const marginRight = 20;
  const marginBottom = 30;
  const marginLeft = 40;

  // Declare the x (horizontal position) scale.
  const x = d3.scaleLinear()
      .domain([0, getMax(df_annot, x_val)+0.5]) // use same dimensions for annot
      .range([marginLeft, width - marginRight]);

  // Declare the y (vertical position) scale.
  const y = d3.scaleLinear()
      .domain([0, getMax(df_annot, y_val)+0.5]) // use same dimensions for annot
      .range([height - marginBottom, marginTop]);

  // Create the SVG container.
  const svg = d3.create("svg")
      .attr("width", width)
      .attr("height", height)
      .attr("id", "svg_volcano"); // give it an ID so I can remove and refresh


  // Add the x-axis.
  svg.append("g")
      .attr("transform", `translate(0,${height - marginBottom})`)
      .call(d3.axisBottom(x));

  // Add the y-axis.
  svg.append("g")
      .attr("transform", `translate(${marginLeft},0)`)
      .call(d3.axisLeft(y));



  // Append the SVG element.
  div_volcano.append(svg.node());

  // mouseover text
  const point_vals = d3.select("#div_volcano")
    .append("p")
    .attr("align", "left")
    .attr("id", "point_vals_volcano")
    .text("Mouseover points for more info, and click to show Pathway Network!");

  // Add the scatterplot
  svg.selectAll(".dots")
      .data(df_subv)
    .enter().append("circle")
      .attr("class", "dots")
      .attr("fill", d => d.type === "A"? "steelblue":"orangered")
      .attr("fill-opacity", 0.3)
      .attr("r", 5)
      .attr("cx", d => x(d[x_val]) )
      .attr("cy", d => y(d[y_val]) )
      .on("mouseover", function(d){
         d3.selectAll(".dots").attr("r", 5) //make sure all the dots are small
         d3.select(this)
          .transition(bounce_select)
          .attr("r", 10);
        
        // show tooltip
        tooltip.transition().duration(200).style("opacity", .8);		
              tooltip.html("<b/>Pathway: </b>" + d["Pathway.Name"] + '\n' +
                          "-log(P) = " + d[y_val]+ '\n' +
                          x_val + " = " + d[x_val])
                .style("left", (d3.event.pageX) + "px")
                .style("top", (d3.event.pageY) + "px");
      }) // mouseover behavior
      .on("mouseout", function(d){
        // remove tooltip
        tooltip.transition().duration(200).style("opacity", 0);
      }) // mouseout behavior
      .on("click", function(d) {
         //console.log(json)
         console.log( "clicked " + d["Pathway.Name"] + " (" + d["Pathway.ID"] + ")" )
         updateNetwork(d["Pathway.ID"])
      }); // click behavior

}

// updateNetwork()
// Update Network Plot
function clearNetwork() {
  if (document.getElementById("svg_network")) { document.getElementById("svg_network").remove() }
}
function updateNetwork(pthw_id) {
  //console.log(pthw_id)
  
  clearNetwork()
  
  // pull network info
  const df_network = json_network[pthw_id]
  // pull network annotations
  const df_net_anno = json_net_anno[annotMenu.options[annotMenu.selectedIndex].text][subvalueMenu.options[subvalueMenu.selectedIndex].value][pthw_id]
  
  // set up links / nodes objects
  const links = df_network.links;
  const nodes = mergeJSONObjects(df_network.nodes, df_net_anno, 'id'); // merge nodes with node-annotations by id
  //console.log(getMax(nodes, 'graphics_x'))
  
  // color-scale for nodes
  const max_logFC = 3; // logFC will range from -5 to 5 for now
  const nodeColor = d3.scaleSequential().domain([-max_logFC,max_logFC])
  .interpolator(d3.interpolateRgbBasis(["#2166AC", "#F7F7F7", "#B2182B"])); // khroma BuRd palette
  
  // node size
  const node_size = 10
  console.log('test')
  
  // get width of container object
  const containerWidth = document.querySelector('.parent').offsetWidth
  const containerHeight = window.innerHeight
  
  // set the dimensions and margins of the graph
  const margin = {top: 10, right: 30, bottom: 30, left: 40},
    width = containerWidth/2*0.95 - margin.left - margin.right,
    height = containerHeight/3 - margin.top - margin.bottom;
  
  // Create the scales for x and y
  const xScale = d3.scaleLinear()
    .domain([d3.min(nodes, d => d.graphics_x), d3.max(nodes, d => d.graphics_x)])  // Domain from data's min and max x values
    .range([0, width]);  // Range from 0 to the SVG width
  const yScale = d3.scaleLinear()
    .domain([d3.min(nodes, d => d.graphics_y), d3.max(nodes, d => d.graphics_y)])  // Domain from data's min and max y values
    .range([height, 0]);  // Range from SVG height to 0 (SVG's y axis is reversed)
  
  // append the svg object to the body of the page
  const svg = d3.select("#div_network")
  .append("svg")
    .attr("width", width + margin.left + margin.right)
    .attr("height", height + margin.top + margin.bottom)
      .attr("id", "svg_network") // give it an ID so I can remove and refresh
  .append("g")
    .attr("transform",
          "translate(" + margin.left + "," + margin.top + ")");


  
  // Define the arrow marker
  svg.append("defs")
    .append("marker")
    .attr("id", "arrowhead")
    .attr("viewBox", "0 -5 10 10") // the bounding box for the arrowhead
    .attr("refX", 20) // position of the arrow relative to the line
    .attr("refY", 0)
    .attr("orient", "auto")
    .attr("markerWidth", 6)
    .attr("markerHeight", 6)
    .append("path")
    .attr("d", "M0,-5L10,0L0,5") // the path to draw the arrow
    .attr("class", "arrowhead");
  
  

  
  
  // Create links (lines connecting nodes)
  svg.selectAll(".link")
    .data(links)
    .enter().append("line")
    .style("stroke", "#aaa")
    .attr("class", "link")
    .attr("x1", d => xScale(nodes[nodes.map(e => e['id']).findIndex(n => n == d.source)].graphics_x))
    .attr("y1", d => yScale(nodes[nodes.map(e => e['id']).findIndex(n => n == d.source)].graphics_y))
    .attr("x2", d => xScale(nodes[nodes.map(e => e['id']).findIndex(n => n == d.target)].graphics_x))
    .attr("y2", d => yScale(nodes[nodes.map(e => e['id']).findIndex(n => n == d.target)].graphics_y))
    .attr("marker-end", "url(#arrowhead)");;
  
  // Initialize the nodes
  //console.log(nodes)
  //console.log(nodes[1].graphics_type)
  const node = svg.selectAll(".node")
    .data(nodes)
    //.enter().append("circle")
    .enter().append(d => d.graphics_type === 'circle'
                    ? document.createElementNS(d3.namespaces.svg, "circle")
                    : document.createElementNS(d3.namespaces.svg, "rect"))
    .attr("class", "node")
    //.style("fill", "#69b3a2")
    .style("fill", function(d) { 
      const hits = d["hits.all"];
      const value = d["logFC.absmax"];
      //console.log(hits)
      if (value != null) {
        return nodeColor(value); // use color-scale otherwise
      } else {
        return "#BBBBBB";  // use grey if the value is null / undefined
      }
    })
  // circle coords / aesthetics
    .attr("cx", d => d.graphics_type === 'circle' ? xScale(d.graphics_x) : null)
    .attr("cy", d => d.graphics_type === 'circle' ? yScale(d.graphics_y) : null)
    .attr("r", node_size/2 )  // Set radius for circles
  // square coords / aesthetics
    .attr("x", d => d.graphics_type === 'circle' ? null : xScale(d.graphics_x)-node_size/2)
    .attr("y", d => d.graphics_type === 'circle' ? null : yScale(d.graphics_y)-node_size/2)
    .attr("width", node_size) // Set width for squares
    .attr("height", node_size) // Set height for squares
    .on("mouseover", function(d){
      // circle behavior
      d3.selectAll(".circles").attr("r", node_size/2) //make sure all the dots are small
      d3.select(this)
        .transition(bounce_select)
        .attr("r", node_size);
      // square behavior
      d3.selectAll(".rect") //make sure all the dots are 
      d3.select(this)
        .transition(bounce_select)
        .attr("x", xScale(d.graphics_x)-node_size) // adjust coords to center
        .attr("y", yScale(d.graphics_y)-node_size)
        .attr("width", node_size*2) // double size
        .attr("height", node_size*2);
      
      // show tooltip
      tooltip.transition().duration(200).style("opacity", .8);		
            tooltip.html("<b/><u/>" + d.graphics_name + '</u></b>\n' +
                         "<b/>Hits In Dataset: </b>" + d['hits.all'] + '\n' +
                         "<b/>Significant Hits: </b>" + d['hits.sign'] + '\n' +
                         "<b/>LogFC Values: </b>" + d['logFC.all.sign'])
              .style("left", (d3.event.pageX) + "px")
              .style("top", (d3.event.pageY) + "px");
    }) // mouseover behavior
    .on("mouseout", function(d){
      // circle behavior
      d3.selectAll(".circles") //make sure all the dots are small
      d3.select(this)
        .transition(bounce_select)
        .attr("r", node_size/2);
      // square behavior
      d3.selectAll(".rect") //make sure all the dots are 
      d3.select(this)
        .transition(bounce_select)
        .attr("x", xScale(d.graphics_x)-node_size/2)
        .attr("y", yScale(d.graphics_y)-node_size/2)
        .attr("width", node_size)
        .attr("height", node_size);
      // remove tooltip
      tooltip.transition().duration(200).style("opacity", 0);
    }) // mouseout behavior
  
}

```



***

# Parameters
    
Details about the parameters listed in **Table `r tab_count`** can be found in the [PANOPLY WIKI](https://github.com/broadinstitute/PANOPLY/wiki/Data-Analysis-Modules%3A-panoply_mo_nmf).    
    
```{r params, include=TRUE, echo=FALSE, warning=T, message=F}
tab_param <- data.frame(param=names(opt), value=unlist(opt))
## insert table
tab_param %>%
      kbl(row.names =FALSE, caption=paste0('**Table ', tab_count,'**: List of parameters used in ```panoply_metaboanalyst```.')) %>%
      kable_paper('hover', full_width = F) 
```
```{r echo=F}
## increment
tab_count <- tab_count + 1
```

<br>

***

**_Created on `r Sys.time()`_**

***

<br>
